Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-13 02_Paper/paper.tex
Update paper.tex

The demonstration cell is a demonstrator representing a general assembly process
and is essentially composed of assembly lines, a universal robot and a wide
range of sensor technology. The following use case is implemented:
shown is a stylized assembly process where two disks are to be stacked on top of each other.
The quality of the pseudo products is predicted on the basis of the concentricity of both
parts to be joined and the optimum operating point. The demonstration cell is configured to 
imitate certain situations that occur in real applications. For example, it is possible to 
simulate failures in the motors, problems with the conveyor belts or incorrect
positioning of an object by the robot arm, which causes anomalies in the vibration sensors,
temperature rise, fluctuations in the air pressure system and other deviations. 
Due to its manageable size and high degree of scalability,
findings gained with the demonstration cell can be transferred to various real
assembly processes and use cases.

>>>>

In our work we applied a case-based research approach to answer the research question. One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance. %This sentence can be deleted if needed.
In addition case-based research approahes have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....). %@Lennart: hier müssen entsürechend Beispiele eingetragen werden
Our case is a production demonstration cell composed of conveyer belts, a universal robot and a wide range of sensor technology. The demonstration cell is executing an stylized assembly process where two disks are to be stacked on top of each other. 
The quality of the pseudo products is evaluated via the concentricity of both
parts to be assembled. The demonstration cell is configured to imitate certain situations that occur in real applications. For example, it is possible to 
simulate failures in the motors, problems with the conveyor belts or incorrect positioning of an object by the robot arm, which causes anomalies in the vibration sensors, temperature rise, fluctuations in the air pressure system and other deviations. Based on the sensor values and process parameters want to predict the concentricity of the assembled parts prior to actual the quality check. 
Due to its manageable size and high degree of scalability,
findings gained with the demonstration cell can be transferred to various real
assembly processes and use cases.
